Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1) \note{\scriptsize Authors, please add/check middle initials and affiliations}

### 2014-04-22 WSSSPE1_report/WSSSPE1_summary_report.tex
Adds endpoint and license comments to sust. def.
These were in the Developing Software section, but hadn't fully carried over
here yet.

Attendees suggested that having a definition of sustainability on
which the community can agree is key.  A related question that was
raised is what the goal of sustainability should be, with a wide range
of possible answers, including more reproducible science, software
persistence, and quality.  And given a goal of sustainability, how
would success in achieving it be measured?  How would one know that a
piece of software has reached sustainability? As a commenter
suggested, this may mean that sustainability should be addressed
throughout the full software life cycle.  It was also pointed out that
software sustainability is not isolated from other attributes of
scientific software and its use, such as usability, and provenance.

>>>>

Attendees suggested that having a definition of sustainability on
which the community can agree is key.  A related question that was
raised is what the goal of sustainability should be, with a wide range
of possible answers, including more reproducible science, software
persistence, and quality.  And given a goal of sustainability, how
would success in achieving it be measured?  How would one know that a
piece of software has reached sustainability? Participants pointed out
that for truly sustainable software there should be no endpoint at
which sustainability can be claimed, because the software products
would continue to be used and useful beyond the single institution,
grant, and developer or development team that created them. This may
mean that sustainability needs to be addressed throughout the full
software life cycle.  It was also pointed out that software
sustainability is not isolated from other attributes of scientific
software and its use, such as usability, and provenance. Similarly,
the question was considered, albeit only briefly, whether proprietary
versus open-source license plays a role in the context softwara
sustainability. For example, should a project ensure that it uses an
OSI-approved license so that software products can outlive any single
entity if they remain important.
